---
title: "R_Week_9_Hmw_607_Web_APIs_Daniel_Thonn"
output: html_document
course: R-607 CUNY MSDA program

---

** Assignment 607_Homework: R_Week_9d_Hmw_607_Web_APIs_Daniel_Thonn **

Summary of Assignment
This assignment involves using Web APIs to obtain information from the New York Times

This Assignment requires the following:

1). R-Studio

The following R-packages are used:
1.tidyr
2.dplyr
3.ggplot2 
4.httr
5.tidyjason
6.data.table

Steps to reproduce:
1). run the R-Studio file: R_607_Week_9d_Hmk_Web_APIs_Daniel_Thonn.Rmd


Setting up and Preparing the Environment

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the libraries needed

```{r, echo=TRUE}


#library(stringr)
library(tidyr)

#install.packages("dplyr")
library(dplyr)

#install.packages("ggplot2")
library(ggplot2)

#install.packages("httr")
library(httr)

#install.packages("tidyjson")
library(tidyjson)

#install.packages("data.table")
library(data.table)


```

Obtain the Top Stories information from the New York Times API

```{r, echo=TRUE}


# Store the api obtained from the New York Times developer website
nyt_api_key_1 <- "7ab87a92a91243eab8de8d7a867f1fa2"


# create the url interface
url_1 <- paste0("https://api.nytimes.com/svc/topstories/v2/home.json?")
url      <- paste0(url_1,"&api-key=", nyt_api_key_1)


# Obtain the results using the the API
contents_1 <- GET(url = url)
contents_1

# store the json information
json_1 <- httr::content(contents_1, type = "text", encoding = "UTF-8")
json_1

# check status
status <- 
   json_1 %>% 
   enter_object("status") %>%
   append_values_string("status") %>% 
   select(status)
status


nyt_top_stories_json <- json_1 %>% as.tbl_json

nyt_top_stories_json

str(nyt_top_stories_json)

head(nyt_top_stories_json)


results2 <-
       nyt_top_stories_json %>%
       enter_object("results") %>%
       gather_array %>%
             spread_values(
            section = jstring("section") ,
            subsection = jstring("subsection") ,
            title = jstring("title"),
            abstract = jstring("abstract"),
            by = jstring("byline"),
            url = jstring("url"),
            item_type = jstring("item_type"),
            updated_date = jstring("updated_date"),
            created_date = jstring("created_date"),
            published_date = jstring("published_date")
        )

results3 <- as.data.frame(results2)

str(results3)

head(results3)

names(results3)
results3$section


```

Graph the Top Story sections by subect in the Top Stories dataframe


```{r, echo=TRUE}
#count of section subjects
sections2<-select(results3,section)

sections3<-data.frame(table(sections2$section))

names(sections3)<-c("Var1","Freq")
head(arrange(sections3,desc(Freq)), n=10)
names(sections3)[1] <- "Section_Subject"
names(sections3)



qplot(data = subset(sections3, Freq>1), x = reorder(Section_Subject, -Freq), y=Freq, xlab="Section_Subject", ylab="Frequency", main = "Section_Subject by Frequency", size=I(5)) +
      theme(text = element_text(),
        axis.text.x = element_text(angle=90, vjust=1)) 


```

Conclusion: The Top Stories information was downloaded successfully from the New York Times developer API site.

The plot shows the numbers of articles by section subject.  This shows that articles by subject US was the largest number of stores, followed in order by Business Day, Opinion, Movies, and World at the time of this download.



**END**
